\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Tilak Ram} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 820-***-**** ~
    \href{mailto:tilak****@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tilak******@gmail.com}} ~ 
  \href{https://www.linkedin.com/in/tilakdevx/}{\raisebox{-0.2\height}{\faLinkedin} LinkedIn} ~
    \href{https://github.com/tilakDevX}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
    \href{https://tilakdevx.github.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{0pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Full-Stack Developer with 3+ years of experience building scalable, production-grade web applications. Delivered a real-time vehicle telematics platform (2,000+ GPS events/sec) and contributed to enterprise compliance and AI-powered solutions. Skilled in Python, Django, React.js, PostgreSQL, Redis, and integrating LLM-powered capabilities into full-stack production systems.}
\vspace{0pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {KPMG India}{Feb 2025 -- Present}
      {\textbf{Full Stack Developer} $|$ KCRA — KPMG Compliance Reporting Assessor}{Gurgaon, India}
      \resumeItemListStart
        \resumeItem{Architected Django/DRF backend with a layered pattern (Controller → Service → Repository) and RBAC across 6 user roles (Super User, Company Admin, CXO, Legal Admin, Auditor, Owner/Escalator chain) in multi-tenant compliance workflows.}
        \resumeItem{Built async Excel report generation with Celery + Redis, returning HTTP 202 immediately while background workers process 50,000+ records.}
        \resumeItem{Implemented immutable audit trail using PostgreSQL transactions — every compliance status change recorded atomically with actor, timestamp, and reason across a 3-stage approval chain (Owner → Escalator → Auditor).}
        \resumeItem{Designed a dual-source LLM-powered chatbot with intent-based routing — Text-to-SQL engine (multi-layer classification, dynamic schema injection, RBAC filters, SQL safety guardrails) for live compliance data queries, and a RAG pipeline for natural language queries over the tool's internal knowledge base.}
        \resumeItem{Automated nightly compliance deadline checks via Celery Beat and integrated E-sign functionality into document approval workflows; configured Apache2 as a reverse proxy for production deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {AutoPeepal Technologies Pvt. Ltd}{Sep 2023 -- Jan 2025}
      {\textbf{MERN Stack Developer} $|$ Vehicle Telematics Platform (Wikitrac)}{Pune, India}
      \resumeItemListStart
        \resumeItem{Built real-time GPS ingestion pipeline processing 2,000+ events/sec using Apache Kafka with 3 independent consumers: alert detection, live dashboard, and trip logging.}
        \resumeItem{Designed WebSocket live dashboard (Socket.io + Redis pub/sub) supporting 500+ concurrent users with sub-second location refresh.}
        \resumeItem{Implemented geofence breach and speed alert system with Redis-cached geofence data, reducing PostgreSQL query load by 80\%.}
        \resumeItem{Containerised and deployed full stack on DigitalOcean with Docker and Nginx reverse proxy; tuned Kafka consumer parallelism for sustained high throughput.}
        \resumeItem{Recognised as \textbf{Outstanding Performer} at AutoPeepal Technologies for contributions to the Wikitrac telematics platform.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\vspace{-15pt}
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript (ES6+)} \\
     \textbf{Backend}{: Django, Django REST Framework, FastAPI, Celery, Node.js, Express.js} \\
     \textbf{Frontend}{: React.js, Redux Toolkit, HTML5, CSS3} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Redis} \\
     \textbf{Messaging \& Realtime}{: Apache Kafka, WebSocket (Socket.io)} \\
     \textbf{AI \& LLM}{: LLM Integration, Text-to-SQL, RAG Pipelines, Prompt Engineering} \\
     \textbf{DevOps \& Cloud}{: Docker, Nginx, Apache2, AWS, Azure, DigitalOcean, CI/CD (Azure Pipelines)} \\
     \textbf{Tools}{: Git, Postman, VS Code} \\
    }}
 \end{itemize}

\vspace{-14pt}
%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{digiSOP — Digital SOP Management Tool} $|$ \emph{FastAPI, React.js, PostgreSQL, Redis, Celery}}{KPMG India}
      \resumeItemListStart
        \resumeItem{Built end-to-end solo — a production-grade platform to author, version, and distribute Standard Operating Procedures digitally, replacing manual paper-based workflows.}
        \resumeItem{Implemented multi-stage approval chains with role-based access, user request management, and version control — ensuring every SOP change is tracked and auditable.}
        \resumeItem{Built RACI matrix tracking and reader acknowledgement system — ensuring accountability across process owners, contributors, and readers.}
        \resumeItem{Async background processing via Celery + Redis for notifications and approval triggers; POC successfully converted into a client-adopted product.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{-10pt}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Science (BSc) — Mathematics \& Computer Application}{Nov 2020 -- Jun 2023}
      {Shiv Harsh Kisan Degree College Basti}{Basti, India}
  \resumeSubHeadingListEnd
\vspace{0pt}

\end{document}